%------------------------
% Resume Template
% Author : Saiprasad Rao
% Github : https://github.com/thesaiprasadrao
% License : DSCE
%------------------------

\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{xcolor}
\hypersetup{
    colorlinks,
    linkcolor={black},
    citecolor={blue!50!black},
    urlcolor={black}
}
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}


  \textbf{{\LARGE Saiprasad Rao}} & Email: \href{mailto:saiprasadrao1234@gmail.com}{saiprasadrao1234@gmail.com}\\
  \underline{\href{https://leetcode.com/u/thesaiprasad/}{Leetcode}} & \underline{\href{https://www.linkedin.com/in/saiprasad-rao-947458212/}{LinkedIn}} \\
  \underline{\href{https://github.com/thesaiprasadrao}{Github: thesaiprasadrao}} & Mobile:~~~+91-990-245-0514\\
  \underline{\href{https://linktr.ee/saiprasadrao}{Linktree}}
\end{tabular*}

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Dayananda Sagar College Of Engineering}{CGPA: 7.5}
        {Bachelor of Engineering - Computer Science And Business Systems}{2023 - 2027}
      \vspace{-5pt}
    \resumeSubHeadingListEnd
	    
\vspace{-5pt}
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    \textbf{Languages}{: C++, Java, Python, JavaScript, HTML, CSS, Shell Scripting}

    \textbf{Technologies/Frameworks}{: React.js, face-api.js}

    \textbf{AI/ML}{: Machine Learning (dataset preprocessing, model training), Computer Vision, }

    \textbf{Databases/Storage}{: MySQL, MongoDB }

    \textbf{DevOps/Deployment}{: Git, GitHub, Jenkins, Jupyter Notebook}

    \textbf{Operating Systems/CLI}{: Linux (Void, Ubuntu), vi Editor, Unix Command-line Tools, Regular Expressions}
    
 \end{itemize}

 \vspace{-10pt}


%-----------PROJECTS-----------------

\section{Projects}
\resumeSubHeadingListStart

\resumeSubItem{\textbf{BlueMesh – Bluetooth Mesh Messaging App} $|$ \emph{Java, Android SDK, Bluetooth API}
}{
\begin{itemize}
\item Developed an \textbf{offline peer-to-peer messaging application} where devices form a \textbf{mesh network} over Bluetooth to relay messages across multiple hops.
\item Implemented \textbf{automatic device discovery}, connection management, and message routing without requiring internet access or continuous app activity.
\item Designed a \textbf{robust message queue system} to ensure delivery reliability, even with intermittent connections.
\item Created a lightweight, \textbf{battery-efficient communication protocol} optimized for short-range, low-latency messaging.
\item Tested across multiple Android devices to validate \textbf{network range extension} through intermediate relay nodes.
\item Targeted use cases include \textbf{disaster recovery, remote areas, and secure offline communication}.
\end{itemize}
}

\resumeSubItem{\textbf{Jee Mains College Predictor} $|$ \emph{Python, Scikit-learn, Pandas, NumPy}
}{
\begin{itemize}
\item Developed an \textbf{end-to-end machine learning system} to predict college admission cutoff ranks using \textbf{40,000+ historical admission records} from 2020–2024 across multiple NITs , IIIts and GFTIs.
\item Implemented and compared multiple ML algorithms (\textbf{Random Forest, Gradient Boosting, Linear Regression, Ridge Regression}) with hyperparameter tuning and cross-validation to achieve optimal accuracy.
\item Built a comprehensive \textbf{data processing pipeline} with categorical encoding, feature engineering, and validation for features including institute type, branch, category, quota, and gender preferences.
\item Designed a \textbf{command-line interface} for personalized college recommendations with confidence intervals based on rank and preferences.
\item Enabled \textbf{model persistence} using joblib for quick deployment without retraining.
\end{itemize}
}
\vspace{-10pt}



\resumeSubItem{\textbf{Face Detection Based Attendance System} $|$ \emph{JavaScript, face-api.js, HTML, CSS}
}{
\begin{itemize}
\item Built a system to \textbf{capture a single classroom image}, detect and identify faces, and \textbf{automatically log attendance}.
\item Leveraged \textbf{face-api.js} for facial detection and recognition on static images.
\item Designed features for \textbf{grievance handling}, including \textbf{student-side functionality via Telegram bot} for re-evaluation requests.
\item Integrated an \textbf{admin panel} for timetable management and student image uploads.
\end{itemize}
}
\vspace{-10pt}

\resumeSubItem{\textbf{OneVote – Real-Time Voting Platform} $|$ \emph{React.js, Node.js, Express, MongoDB, HTML, CSS, JavaScript}
}{
\begin{itemize}
\item Designed and developed a secure, user-friendly \textbf{online voting platform} to facilitate \textbf{real-time polling and result tracking}.
\item Implemented the \textbf{frontend} using \textbf{HTML, CSS, and JavaScript (React)} for intuitive, responsive, and accessible user interfaces.
\item Built the \textbf{backend} with \textbf{Node.js and Express}, integrating \textbf{MongoDB} for efficient data storage and retrieval of votes and poll data.
\item Incorporated \textbf{authentication and encryption protocols} to ensure vote integrity and user privacy.
\item Developed additional features including \textbf{real-time vote updates} and \textbf{admin dashboards} for poll management.
\end{itemize}
}
\vspace{-10pt}


\resumeSubHeadingListEnd
\vspace{-10pt}

\end{document}