%------------------------
% Resume Template
% Author : Saiprasad Rao
% Github : https://github.com/thesaiprasadrao
% License : MIT
%------------------------

\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{xcolor}
\hypersetup{
    colorlinks,
    linkcolor={black},
    citecolor={blue!50!black},
    urlcolor={black}
}
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Saiprasad Rao}} & Email: \href{mailto:saiprasadrao1234@gmail.com}{saiprasadrao1234@gmail.com}\\
  \underline{\href{https://leetcode.com/u/thesaiprasad/}{Leetcode: thesaiprasad}} & \underline{\href{https://www.linkedin.com/in/saiprasad-rao-947458212/}{LinkedIn}} \\
  \underline{\href{https://github.com/thesaiprasadrao}{Github: thesaiprasadrao}} & Mobile:~~~+91-9902450514\\
  \underline{\href{https://linktr.ee/saiprasadrao}{Linktree}}
\end{tabular*}

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Dayananda Sagar College Of Engineering}{CGPA: 7.2}
        {Bachelor of Engineering - Computer Science And Business Systems}{2023 - 2027}
      \vspace{-5pt}
    \resumeSubHeadingListEnd
	    
\vspace{-5pt}
\section{Technical Skills And Interests}
 \begin{itemize}[leftmargin=0.15in, label={}]
    {\small \item
    \textbf{Languages:} C++(Proficient) , Java , Python , TypeScript \\
    \textbf{Frameworks:} React.js \\
    \textbf{Databases:} MySQL , MongoDB \\
    \textbf{DevOps:} Git , GitHub \\
    \textbf{Relevant Coursework: } Data Structures \& Algorithms, Operating Systems, Object Oriented Programming, Database Management System, Software Engineering, Computer Networks.\\
    \textbf{APIs:} RESTful APIs, JSON handling 

 \end{itemize}

 \vspace{-10pt}

%-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading{\textbf{BlueMesh - Bluetooth-based Peer-to-Peer Messaging App} $|$ \emph{Node.js, Web Bluetooth API, LocalStorage}}{}
\resumeItemListStart
  \resumeItem{Built a \textbf{browser-based chat app} that connects devices directly over \textbf{Bluetooth}, eliminating the need for internet or mobile data.}
  \resumeItem{Implemented \textbf{multi-hop message relaying}, allowing messages to travel across intermediate devices and effectively extending range.}
  \resumeItem{Designed the system to be \textbf{offline-first}, ensuring 100\% local storage of messages and files with automatic reconnection after disconnections.}
  \resumeItem{Packaged and tested the app on Android using \textbf{Node.js + Termux}, enabling deployment without external servers or infrastructure.}
\resumeItemListEnd
\vspace{-16pt}

\resumeProjectHeading{\textbf{JEE Mains College Predictor} $|$ \emph{Python, Scikit-learn, Pandas, NumPy}}{}
\resumeItemListStart
  \resumeItem{Built an \textbf{ML-based cutoff prediction tool} trained on \textbf{2,00,000+ cut-off records} (2020–2024) from NITs, IIITs, and GFTIs.}
  \resumeItem{Compared \textbf{Random Forest, Gradient Boosting, and Ridge Regression}, improving prediction accuracy by \textbf{12\%} through hyperparameter tuning.}
  \resumeItem{Created features (branch, category, quota, gender) and applied \textbf{categorical encoding} to improve model generalization on unseen ranks.}
  \resumeItem{Created a \textbf{CLI interface} that provides college recommendations within seconds, with confidence intervals for rank predictions.}
  \resumeItem{Optimized workflow by saving trained models with \textbf{joblib}, reducing inference latency by \textbf{80\%} without retraining.}
\resumeItemListEnd
\vspace{-26pt}

\resumeProjectHeading{\textbf{OneVote – Real-Time Voting Platform} $|$ \emph{React.js, Node.js, Express, MongoDB}}{}
\resumeItemListStart
  \resumeItem{Developed a secure \textbf{web-based polling app} that supported \textbf{100+ concurrent users} with real-time vote updates.}
  \resumeItem{Built a \textbf{responsive frontend} that works well on both mobile and desktop devices.}
  \resumeItem{Designed a scalable \textbf{Node.js + Express backend} with \textbf{MongoDB}, handling creation and storage of 1,000+ polls.}
  \resumeItem{Integrated \textbf{authentication and encryption}, ensuring vote integrity and protecting user identities.}
  \resumeItem{Shipped an \textbf{admin dashboard} for managing polls and monitoring live results with low latency.}
\resumeItemListEnd
\vspace{-16pt}

\resumeProjectHeading{\textbf{Mood Diary – Privacy-First Journal App} $|$ \emph{HTML, CSS, Vanilla JavaScript}}{}
\resumeItemListStart
  \resumeItem{Developed a client-side journaling app with \textbf{100\% local storage} – no data ever leaves the user's device.}
  \resumeItem{Created interactive journaling interface with contextual writing prompts and animated visual feedback.}
  \resumeItem{Added mood tracking analytics with distribution charts and smart date formatting (Today/Yesterday/specific dates).}
  \resumeItem{Optimized with CSS animations and micro-interactions for \textbf{sub-100ms response times} and smooth user experience.}
\resumeItemListEnd

\resumeSubHeadingListEnd
 \vspace{-10pt}

%-----------ACHIEVEMENTS-----------------
\section{Coding \& Achievements}
\resumeItemListStart
  \resumeItem{\textbf{CodeChef:} 1-star rating with peak rating of 1400}
  \resumeItem{\textbf{LeetCode:} Solved 100+ algorithmic problems across various difficulty levels}
  \resumeItem{\textbf{Competitive Programming:} Active participant in online coding contests}
\resumeItemListEnd

\end{document}